Reproduction

### 2024-10-25 pages/reproduction.qmd
docs(reproduction): add johnson

**@johnson_cost_2021:** TBC <!-- TODO: Add Johnson -->

@@

| Study | Scope | Success | Time |
| --- | --- | --- | --- |
| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94%) | 28h 14m |
| Huang et al. 2019 | 8 items:<br>• 5 figures<br>• 3 in-text results | 3 out of 8 (37.5%) | 24h 10m |
| Lim et al. 2020 | 9 items:<br>• 5 tables<br>• 4 figures | 9 out of 9 (100%) | 12h 27m |
| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 14h 42m |
| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | <!--TODO--> | <!--TODO--> |
| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | 1 out of 8 (12.5%) | 17h 56m |
| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | 5 out of 5 (100%) | 3h 50m |

@@

<!-- TODO: Add Johnson et al. 2021 once conducted reproduction -->

@@

# Johnson et al. 2021
# TODO: Add times once completed reproduction

@@

# Create list with the dataframes, labels and colours, to use for each plot
to_plot = [
    (df_sho, 'Shoaib and<br>Ramamohan<br>2022', '#ee6677'),
    (df_hua, 'Huang et<br>al. 2019', '#228833'),
    (df_lim, 'Lim et<br>al. 2020', '#4477aa'),
    (df_kim, 'Kim et<br>al. 2021', '#ccbb44'),
    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee'),
    # (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
    (df_her, 'Hernandez<br>et al. 2015', '#882255'),
    (df_woo, 'Wood et al.<br>2021', '#117733')
]
```

>>>>

**@johnson_cost_2021:** This study uses a previously validated discrete-event simulation model, EPIC: Evaluation Platform in chronic obstructive pulmonary disease (COPD). The model is written in **C++** with an **R** interface, using R scripts for execution. The model is adapted to evaluate the cost-effectiveness of 16 COPD case detection strategies in primary care, comparing costs, quality-adjusted life years (QALYs), incremental cost-effectiveness ratios (ICER), and incremental net monetary benefits (INMB) across scenarios. Sensitivity analyses are also conducted. <a href="https://pythonhealthdatascience.github.io/stars-reproduce-johnson-2021/evaluation/reproduction_success.html" target="_blank">Link to reproduction.</a>

@@

| Study | Scope | Success | Time |
| --- | --- | --- | --- |
| Shoaib and Ramamohan 2022 | 17 items:<br>• 1 table<br>• 9 figures<br>• 7 in-text results | 16 out of 17 (94%) | 28h 14m |
| Huang et al. 2019 | 8 items:<br>• 5 figures<br>• 3 in-text results | 3 out of 8 (37.5%) | 24h 10m |
| Lim et al. 2020 | 9 items:<br>• 5 tables<br>• 4 figures | 9 out of 9 (100%) | 12h 27m |
| Kim et al. 2021 | 10 items:<br>• 3 tables<br>• 6 figures<br>• 1 in-text result | 10 out of 10 (100%) | 14h 42m |
| Anagnostou et al. 2022 | 1 item:<br>• 1 figure | 1 out of 1 (100%) | 2h 11m |
| Johnson et al. 2021 | 5 items:<br>• 1 table<br>• 4 figures | 4 out of 5 (80%) | 19h 49m |
| Hernandez et al. 2015 | 8 items:<br>• 6 figures<br>• 2 tables | 1 out of 8 (12.5%) | 17h 56m |
| Wood et al. 2021 | 5 items:<br>• 4 figures<br>• 1 table | 5 out of 5 (100%) | 3h 50m |

@@

<!--TODO: Consider changing this figure to have lines straight directly connecting points rather than steps, as that would prevent overlap between hernandez and wood? However, time to event data is usually plot like that. -->

@@

# Johnson et al. 2021
time_joh = [
    [1124, 'Table 3'],
    [1124, 'Figure 3'],
    [1189, 'Figure 4'],
    [np.nan, 'Appendix 6'],
    [1157, 'Appendix 7']]
df_joh = process_times(time_joh)

@@

# Create list with the dataframes, labels and colours, to use for each plot
to_plot = [
    (df_sho, 'Shoaib and<br>Ramamohan<br>2022', '#ee6677'),
    (df_hua, 'Huang et<br>al. 2019', '#228833'),
    (df_lim, 'Lim et<br>al. 2020', '#4477aa'),
    (df_kim, 'Kim et<br>al. 2021', '#ccbb44'),
    (df_ana, 'Anagnostou<br>et al. 2022', '#66ccee'),
    (df_joh, 'Johnson et<br>al. 2021', '#aa3377'),
    (df_her, 'Hernandez<br>et al. 2015', '#882255'),
    (df_woo, 'Wood et al.<br>2021', '#117733')
]
```
